---
title: "Homework 1"
subtitle: "Research Methods, Spring 2024"
author: "Ria Dharnidharka"
format:
  pdf:
    output-file: "dharnidharka-r-hwk1-3"
    output-ext:  "pdf"
    header-includes:
      - \usepackage{float}
      - \floatplacement{table}{H}
---
```{r}
#| include: false

if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, readr, readxl, hrbrthemes, fixest,
               scales, gganimate, gapminder, gifski, png, tufte, plotly, OECD,
               ggrepel, survey, foreign, devtools, pdftools, kableExtra, modelsummary,
               kableExtra)
```
```{r}
#| include: false
#| eval: true
 
load("Hwk1_workspace.Rdata")
```

\newpage
# Enrollment Data
Answer the following based on the enrollment data:

\vspace{.2in}
\noindent 1. How many observations exist in your current dataset?<br>

In the current dataset, there are 13,276,162 total observations. 

\newpage
\noindent 2. How many different *plan_types* exist in the data? <br>

There are 18 total different plan types. 

\newpage
\noindent 3. Provide a table of the count of plans under each plan type in each year.<br>

See @tbl-plans.

```{r} 
#| echo: false
#| label: tbl-plans
#| tbl-cap: "Plan types by year"

options(knitr.kable.NA = 0)
knitr::kable(plan.type.year1, 
             col.names=c("Plan Type","2010","2011",
                         "2012","2013","2014","2015"),
             format.args=list(big.mark=","), booktabs = TRUE) %>%
             kable_styling(latex_options=c("scale_down"))
```